\documentclass{report}

\begin{document}
\section*{Valediction}

Ms Hutson, Deacon Iannarino, Mr Urquhart, faculty, parents, friends and fellow
classmates, I welcome you. And at this, the day on which we celebrate our
graduation, I say goodbye. As we the class of two thousand fourteen bid our
\emph{alma mater} farewell, we turn our sights to new endeavors and begin to
select for ourselves a new home in the world.

Our graduation from high school marks a time of many and wonderful changes in
our lives. Of the many changes which might mark a young person's life, none can
match the distinction held by his passage into adulthood, the same transition
marked by our celebration today. Our many years of schooling and
extracurriculars, our stress in the face of exams and our anticipation of
college decisions have all come to pass and their consequence now pales in light
of the journey ahead. 

We now enter the world with a new and excellent credential: we can now call
ourselves Watterson alumni. To be sure, graduation is a day of significance in
any young person's life, but we the graduating class of Bishop Watterson High
School are today endowed with something even grander: we now go forth into the
world armed with a Watterson degree. This degree is the key into college for
many of us, and a workforce-credential for those of us taking different paths,
but more importantly, it is a symbol of our time spent in these halls, the
formative years which we have spent as members of the nurturing Watterson
family. These years were marked by our growth as individuals, our coming
together as a community, and our development into the fruitful leaders and
moral role models who now take the stage as graduates.

These four years have been perhaps the most formative of our lives. We who
entered as a group of timid freshman, largely unfamiliar to one another, now
exit as a tight-knit community, with friendships that will last a lifetime.
Even beyond the walls of Watterson, high school tends to catch its students at
a time of rapid change. In these past four years we transformed from middle
schoolers into adults. We were faced with two hundred strangers, and we managed
to find for ourselves a group with whom we could enjoy these years. We took the
roads as licensed drivers and for the first time, the world now felt a little
smaller. And now, as we go forth from these halls and continue to grow, this
whole world will begin to feel within reach.

Of the many advantages of a Watterson education, none outshines the way in
which she prepares her students for life after high school. Over the past four
years we have been surrounded by remarkable faculty and immersed in a unique
environment, one marked by passion for one's work and compassion for one's
peers. Now we have a responsibility to our school: with degree in hand, we set
out to become role models for those around us, to bear the image of Watterson
in all that we do.

As we take our places in this world, I urge you, members of the graduating
class, to excel; to take the lessons you have learned in these halls, and to
put them to use in the real-world; to live moral lives and to find those people
whose lives you can value above all else; to devise far-fetched dreams, and
seize them; to give your all to this life, and make a name for yourself.

These past four years have been a crazy journey, a time of rapid development
and extreme growth. Now, as we complete our voyage across this bridge from
elementary school to adulthood, we turn to new endeavors, forever altered by
the journey behind us. We go forth as Watterson graduates, prepared to take on
the world and to act in Watterson's name for years to come. Congratulations and
good luck to the graduating class of two thousand fourteen!

\end{document}

